---
title: "RIKOLTO"
output: flexdashboard::flex_dashboard
---


```{r setup, include=FALSE}
library(flexdashboard)
source("color.R")
source("R/rikolto.R")
source("waffle.R")
source("ProductionCommercialization.R")
source("PlanningInvestment.R")
source("Resilience.R")
source("Inclusion.R")
library(DT)
```


Map
=====================================  
 
### Rikolto Participants
    
```{r}
map
```

Demographics 
=====================================     
    
Column {data-width=600}
-------------------------------------
    
### 
    
```{r}
ggplotly(prod_org)
```
   
Column {data-width=400}
-------------------------------------
   
### Chart 2

```{r}
counts %>% 
    DT::datatable()
```   
 
### Chart 3
    
```{r}
ggplotly(age)
```


Production & Commercialization {data-orientation=rows}
=====================================     
   
Row 
-------------------------------------

### Productivity by farmer organization and commodity

```{r}
farmland_plot
```

### Productivity Distribution by commodity

```{r}
ggplotly(p)
```

Row 
-------------------------------------
   
### Commercialized share by commodity

```{r}
ggplotly(commercialization_plot)
```   
    
### Production by farmer organization 

```{r}
ggplotly(l)
```

Planning & Investment {data-orientation=rows}
=====================================     
   
Row 
-------------------------------------

### Drivers of production planning

```{r}
ggplotly(drivers_plot)
```

### Sources of credit

```{r}
access_plot
```

Row 
-------------------------------------
   
### Reasons why no access to credit

```{r}
why_no_acess %>% 
    DT::datatable()
```   
    
### Investment drivers

```{r}
ggplotly(k)
```

Inclusiveness & Gender 
=====================================     
   
Column
-------------------------------------

### Participation in the value chain: Who typically represents the household when trainings are offered?

```{r}
ggplotly(training_plot)
```

### Participation in the value chain - opinion by age and sex: Compared with other members, is your opinion respected/taken into account within your farmer organisation?

```{r}
opinion_plot
```

Column
-------------------------------------
   
### Who controls and decides how the income from the focus crop is used?

```{r}
ggplotly(decisions_plot)
```

Resilience 
=====================================     
   
Column 
-------------------------------------

### Access to Information

```{r}
ggplotly(info_plot)
```

###

```{r}
ggplotly(strategy)
```

Column
-------------------------------------
   
### Intensity and frequency of shock

```{r}
shock %>% 
    DT::datatable()
```   
    
